### 2015-02-27 icfp15-servo/servo.tex
Added myself as an author and made some minor edits.

\subsection{Libraries and abstractions}
Many high-level languages provide abstractions over I/O, threading, parallelism, and concurrency.
Rust provides functionality that addresses each of these concerns, but they are designed as thin
wrappers over the underlying services, in order to provide a predictable, fast implementation
that works across all platforms.
Therefore, much like other modern browsers, Servo contains many of its own specialized implementations of
library functions that are tuned for the specific cases of web browsers.
For example, we have special ``small'' vectors that allow instantiation with a default inline size,
as there are use cases where we create many thousands of vectors, nearly none of which have more than 4~elements.
In that case, removing the extra pointer indirection --- particularly if the values are of less than pointer size ---
can be a significant space savings.
We also have our own work-stealing library that has been tuned to work on the flow tree during the process of layout,
as described in \secref{sec:browsers}.
It is our hope that this code might be useful to other projects as well, though it is fairly browser-specific today.

@@

The Rust compiler can also load compiler plugins written in Rust. These can perform syntactic transformations beyond the capabilities of the hygienic rule-based macros. Compiler plugins use unstable internal APIs, so the maintenance burden is high compared to pattern-based macros. Nevertheless, Servo uses procedural macros for a number of purposes, including building perfect hash maps at compile time,\footnote{\url{https://github.com/sfackler/rust-phf}} interning string literals, and auto-generating GC trace hooks. Despite the exposure to internal compiler APIs, the deep integration with tooling makes procedural macros an attractive alternative to the traditional systems metaprogramming tools of preprocessors and code generators.

>>>>

\subsection{Libraries and abstractions}
Many high-level languages provide abstractions over I/O, threading, parallelism, and concurrency.
Rust provides functionality that addresses each of these concerns, but they are designed as thin
wrappers over the underlying services, in order to provide a predictable, fast implementation
that works across all platforms.
Therefore, much like other modern browsers, Servo contains many of its own specialized implementations of
library functions that are tuned for the specific cases of web browsers.
For example, we have special ``small'' vectors that allow instantiation with a default inline size,
as there are use cases where we create many thousands of vectors, nearly none of which have more than 4~elements.
In that case, removing the extra pointer indirection --- particularly if the values are of less than pointer size ---
can be a significant space savings.
We also have our own work-stealing library that has been tuned to work on the
DOM and flow trees during the process of styling and layout,
as described in \secref{sec:browsers}.
It is our hope that this code might be useful to other projects as well, though it is fairly browser-specific today.

@@

The Rust compiler can also load compiler plugins written in Rust. These can perform syntactic transformations beyond the capabilities of the hygienic pattern-based macros. Compiler plugins use unstable internal APIs, so the maintenance burden is high compared to pattern-based macros. Nevertheless, Servo uses procedural macros for a number of purposes, including building perfect hash maps at compile time,\footnote{\url{https://github.com/sfackler/rust-phf}} interning string literals, and auto-generating GC trace hooks. Despite the exposure to internal compiler APIs, the deep integration with tooling makes procedural macros an attractive alternative to the traditional systems metaprogramming tools of preprocessors and code generators.
